The title

### 2023-03-28 doc/multiverse.Rmd
merge
update assets

@@

moderator_df <- data.frame(
  moderator = c("bmi", "ses", "sex", "weekday", "season", "region", "daylight", "wear_location"),
  moderator_formal = c("BMI", "SES", "sex", "weekday", "season", "region", "daylight hours", "wear location"),
  image_path = c("Bmi", "Ses", "Sex", "Weekday_x", "Season", "Region", "Daylight_hours", "Accelerometer_wear_location")
)
moderator_df$moderator_sentence <- stringr::str_to_sentence(moderator_df$moderator)

@@

  moderator <- moderator_df$moderator[r]
  moderator_fig <- gsub("_","-",moderator)
  moderator_formal <- moderator_df$moderator_formal[r]
  moderator_sentence <- moderator_df$moderator_sentence[r]
  image_path <- moderator_df$image_path[r]

@@

<!------------------------------------>
<!-- Auto-generated chunks go here: -->
<!------------------------------------>
\clearpage

>>>>

## Model diagnostics

The model diagnostics for the main analysis, and for all models presented in this document are in Table \@ref(tab:model-diagnostics)

```{r model-diagnostics}
tar_read(model_diagnostics) |> 
  papaja::apa_table(caption = "Model diagnostics", escape = FALSE,
                    longtable = TRUE)
```

@@

moderator_df <- data.frame(
  moderator = c("bmi", "ses", "sex", "weekday", "season", "region", "daylight", "wear_location"),
  moderator_formal = c("BMI", "SES", "sex", "weekday", "season", "region", "daylight hours", "wear location"),
  image_path = c("Bmi", "Ses", "Sex", "Weekday_x", "Season", "Region", "Daylight_hours", "Accelerometer_wear_location")
)

@@

  moderator <- moderator_df$moderator[r]
  moderator_fig <- gsub("_","-",moderator)
  moderator_formal <- moderator_df$moderator_formal[r]
  image_path <- moderator_df$image_path[r]

@@

<!------------------------------------>
<!-- Auto-generated chunks go here: -->
<!------------------------------------>

\clearpage
